---
title: "hw1"
author: "pengxu"
date: "1/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Stats230 HW1
Matrices and Vector Multiplication, using written function to calculate the product of 2 $n$ dimensional square matrices $A$,$B$ and a $n$ column vector.

```{r matrices_vector_mult}
devtools::install_github('https://github.com/pengxu9/stats230')
library(stats230)
A<- matrix(sample(1:100,100,replace=TRUE),ncol=10)
B<- matrix(sample(1:100,100,replace=TRUE),ncol=10)
x<- c(sample(1:100,10,replace=TRUE))
matrice_vector_mult(A,B,x,matrices=T)
matrice_vector_mult(A,B,x,matrices = F)
```

## microbenchmarking

Microbenchmarking for performance measurement
```{r bench}
bench::mark(
  matrice_vector_mult(A,B,x,matrices=T),
  matrice_vector_mult(A,B,x,matrices = F)
)
```

The final performances result suggests that $A$ $\times ($$B$ $\times$ $x$) is a better way, which takes less memory allocation and less total time spent.


URL of github repository: https://github.com/pengxu9/stats230
